Traffic Collisions in Toronto: Analysis of Key Variables

### 2024-09-24 paper/temp.qmd
intital draft update

---
title: "Traffic Collisions in Toronto: Analysis of Key Variables"
subtitle: "An Analysis of Traffic Collision Data from 2014-2024"
author: 
  - Andy Jiang
thanks: "Code and data are available at: https://github.com/AndyYanxunJiang/toronto-traffic-collisions.git"
date: 24 September 2024
date-format: long
abstract: "This paper analyzes traffic collision data in Toronto from 2014 to 2024. It explores trends in collisions by month, year, and neighborhood, examining variables such as fatalities, injuries, and property damage. The analysis is done using R, with visualizations produced through ggplot2."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Traffic Collisions in Toronto: Analysis of Key Variables"
subtitle: "An Analysis of Traffic Collision Data from 2014-2024"
author: 
  - Andy Jiang
thanks: "Code and data are available at: https://github.com/AndyYanxunJiang/toronto-traffic-collisions.git"
date: today
date-format: long
abstract: "This paper analyzes traffic collision data in Toronto from 2014 to 2024. It explores trends in collisions by month, year, and neighborhood, examining variables such as fatalities, injuries, and property damage. The analysis is done using R, with visualizations produced through ggplot2."
format: pdf
number-sections: true
bibliography: references.bib
---
